---
title: "Homework 2"
author: "Shuqi Hong"
description: "Reading in final project data - avocado.csv"
date: "6/09/2023"
format:
  html:
    toc: true
    code-fold: true
    code-copy: true
    code-tools: true

---

# Introduction

The table below represents weekly 2015 - 2018 retail scan data for National retail volume (units) and price. Retail scan data comes directly from retailers’ cash registers based on actual retail sales of Hass avocados. 

Some relevant columns in the dataset:

Date - The date of the observation
AveragePrice - the average price of a single avocado
type - conventional or organic
year - the year
Region - the city or region of the observation
Total Volume - Total number of avocados sold
4046 - Total number of avocados with PLU 4046 sold
4225 - Total number of avocados with PLU 4225 sold
4770 - Total number of avocados with PLU 4770 sold

I read in file first and delete the first column because it represents row number.
```{r}
#| label: setup
#| warning: false
#| message: false

library(tidyverse)
library(dplyr)
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)

avocado <- read_csv("_data/avocado.csv")

avocado <- avocado %>% select(-1)

avocado

```

I separate "Date" into year, month and day column which shows clearer. Then I sorted them chronologically and mutate the variables. the column of 4046, 4225, 4770 are the size of Hass avocado, respectively small, large, extra large. So I also renamed them. I think I won't analyze this data in each week, so I also delete it.

```{r}
clean_avocado <- avocado %>% select(-`year`) %>% 
  separate(Date, into= c("year","month","day"), sep="-") %>% arrange(year, month, day) %>%
  fill(year,month) %>% 
  mutate( month = case_when(
  month == "01" ~ "January", 
  month == "02" ~ "Feburary",
  month == "03" ~ "March",
  month == "04" ~ "April",
  month == "05" ~ "May",
  month == "06" ~ "June",
  month == "07" ~ "July",
  month == "08" ~ "August",
  month == "09" ~ "September",
  month == "10" ~ "October",
  month == "11" ~ "November",
  month == "12" ~ "December"
)) %>%
  mutate(
    month = as_factor(month),
    day = as_factor(day),
    type = as_factor(type)
  ) %>% 
  rename(c( small = `4046`, `large` = `4225`, `Extra_large` = `4770`)) %>% select(-`day`)
                  
clean_avocado   

glimpse(clean_avocado)
unique(clean_avocado$type)

```

```{r}
clean_avocado <- clean_avocado %>% group_by(year, month, region, type) %>%
  mutate(mean_price_permonth = mean(AveragePrice)) %>% 
  ungroup() %>% 
  group_by(year, region, type) %>%
  mutate(mean_price_peryear = mean(AveragePrice))%>% 
  ungroup() %>% select(-AveragePrice)

clean_avocado #%>%   summarise(mean_AveragePrice = mean(AveragePrice))

```
The original average price is calculated per week which is useless for me. So I caculate the average price of each year and month. 

```{r}

summarise_avocado <- clean_avocado %>% group_by(year, region, type) %>%
  summarise(mean_price_peryear = mean(mean_price_peryear), mean_total_volume = mean(`Total Volume`), mean_total_bags = mean(`Total Bags`) )

summarise_avocado
```

# Potential questions
This table is about the general things which are the average value of price, total volume and total bags in each year. I will plot some graphs about this tabble in the future.

From this table, I will focus on below information in the future. 

1. The change in annual purchase volume of avocados in the whole country.
2. people prefer organic avocados or conventional one. (Analyze it from regions, months and years.)
3. The relationship between the purchase of the size of avocados and purchase of the type of it.
4. The relationship between the purchase of the total volume and average price.
5. Annual change of purchase of the total volume in each region.
6. Each region purchased different size of bags ratios each year.

This is what I think of now, and I will continue to update it in the future.

